%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% % sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
\setlength{\footskip}{5pt}
\begin{center}
    {\Huge \scshape Shaurya Kishore Panwar} \\ \vspace{2pt}
    Machine Learning and Robotics Enthusiast \\ \vspace{3pt}
    \href{mailto:shauryak.panwar@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shauryak.panwar@outlook.com}} ~ 
    \href{https://linkedin.com/in/shaurya-k-panwar/}{\raisebox{-0.2\height}\faLinkedin\ \underline{shaurya-k-panwar}}  ~
    \href{https://github.com/KlrShaK}{\raisebox{-0.2\height}\faGithub\ \underline{KlrShaK}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delhi Technological University}{Dec. 2020 -- Present}
      {Bachelor of Technology in Engineering Physics (Majors in Electronics), CGPA: 8.3/10}{Delhi, India}
    \resumeSubheading
      {St. Xavier's Senior Sec. School}{Dec. 2020 -- Present}
      {Central Board of Secondary Education, Percentage: 89.4\%}{Rohini, Delhi, India}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     % \resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Discrete Structures
%                 \item Machine Learning
%                 \item Algorithms Analysis
%                 \item Database Management
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     % \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Autonomous Systems Intern - Euler Motors}{Jul. 2022 -- Aug. 2022}
      {Advisors: Mr. Gaurav Taank}{Delhi, India}

      
      {Developed Autonomous Stack for Prototype Autonomous Delivery Vehicle for large factories, capable of avoiding dynamic obstacles and simultaneously mapping and planning its optimal path.}
      \vspace*{-2mm}
      \resumeItemListStart
        \resumeItem{Carried out LiDAR-Camera Fusion to generate 3D Semantic Maps from LiDAR Scan, Semantic segmented images are given as input which projects Point-cloud to Image space, extracting RGB information from the Image, back-project it to LiDAR space, and publishes a segmented Point-cloud.}
        \resumeItem{Studied various graph-based SLAM algorithms for real-time mapping and localization. Selected modified RTAB-map for use with Velodyne VLP-16 because of faster inference time and better accuracy and localization capabilities at speed. Carried out generation of sparse-HD 3D map of the environment.}
        \resumeItem{Carried out Sensor Fusion using Extended-Kalman Filters of Wheel Encoders, GPS and IMU to improve localization of our vehicle}
        \resumeItem{Made path detection algorithm robust to noise and error by creating Filtering node for Point-cloud data to remove outliers, downsample received cloud for faster processing and carry out Ground Plane detection in Point-cloud.}
        \resumeItem{Carried out Robot Model Generation (Unified Robotics Description Format) and developed simulation environment in Gazebo for efficient and agile testing of algorithms..}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Startup, Inc}{May 2019 -- August 2019}
    %   {Front End Developer Intern}{City, State}
    %   \resumeItemListStart
    %     \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
    %     \resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
    %     \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
    %     \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.}
    % \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{1pt}
    \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://drive.google.com/drive/folders/1jaOyK1fHZpHoX54Q8uiEvAYqxPnmLSqJ?usp=sharing}{Autonomous Systems Engineer - Team Defianz-DTUSDC } }
      {Dec. 2020 -- Present}
      {Advisors: Prof. Anil S. Parihar \& Prof. Qasim Murtaza }{Delhi, India}
      
      
      {Designing and Developing Autonomous Framework for Open-Wheeled Formula Student Driverless Race car, one of the first driverless team in India. Achieved 8th Position worldwide in FS Italy 2022}
            
      \resumeItemListStart
       {\href{https://drive.google.com/drive/folders/1jaOyK1fHZpHoX54Q8uiEvAYqxPnmLSqJ?usp=sharing}{\textbf{Perception Subsystem} $|$ \emph{Python, TensorFlow, ROS, Darknet-YOLOv4}}}
       \vspace{-2pt}
        \resumeItem{Implemented YOLO V4 after exhaustively literature review of existing object detection algorithms and its performance}
        \resumeItem{Built a CV pipeline capable of operating at high speed to accurately detect, localize and classify traffic cones. Starting from a small dataset (1000 images) with 3 categories, used image augmentation, transfer learning and custom synthetic dataset generation to improve accuracy by 20\%}
        \resumeItem{Carried out extrinsic and intrinsic LiDAR-Camera calibration by projecting LiDAR data onto the image, to simultaneously carry out calibration of camera and LiDAR with an intuitive GUI to pin-point real-time location of cones(obstacles) in the environment}


        \vspace{3pt}
       {\textbf{Model-Based Planning Subsystem} $|$ \emph{Python, C++, Matplotlib, Numpy}}
       \vspace{-2pt}
        \resumeItem{Implemented a model-Based Planning algorithm BayesRace, using Bayesian Optimization to generate optimal Racing Line in just a few seconds, faster than traditional algorithms}
        \resumeItem{After initial Random sampling of trajectories, a Gaussian process model was trained and used Bayesian Optimization to iteratively search for fastest racing line}
        \resumeItem{Implemented a model-Based Planning algorithm BayesRace, using Bayesian Optimization to generate optimal Racing Line in just a few seconds, faster than traditional algorithms}


       \vspace{4pt}       {\href{https://drive.google.com/drive/folders/1YhOIC_EkKafmkKqkXDeokGFuyvxM03B5?usp=share_link}{\textbf{Software/Electronics Subsystem Testing and Architecture Analysis} $|$ \emph{Python, C++, Arduino, UnitTest}}}
       \vspace{-2pt}
        \resumeItem{Carried out rigorous System Level and Autonomous (SIL and HIL) Testing to ensure system reliability}{As Part of FSEV}
        \resumeItem{Presented and proposed implementation of ADAS system for Ather Energy’s electric 2-wheeler}   
      \resumeItemListEnd

      
      \vspace{50pt}
      \newpage
      % \vspace{50pt}
      \resumeProjectHeading
      {\href{https://drive.google.com/drive/folders/1jaOyK1fHZpHoX54Q8uiEvAYqxPnmLSqJ?usp=sharing}{{\textbf {NXP Self Driving Car Model} $|$ \emph{Python, TensorFlow, ROS2, OpenCV}} } }{Aug. 2021}
          \resumeItemListStart
            \resumeItem{Developed a Deep-learning based framework for visual navigation using Imitation Learning in an urban environment laid with obstacles such as pedestrians, barricades and other cars. Deployed End-to-End CNN model with regularization technique with ROS2 in a simulated environment}
            \resumeItem{Developed custom dataset for traffic signs and implemented YOLOV4 tiny for traffic sign detection}
            \resumeItem{Developed custom path planning pipeline in conjunction with using Pure Pursuit for controls, to recognize vehicle state and tackle traffic signs and obstacles}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Age-Invariant Face Recognition} $|$ \emph{Python, TensorFlow, TensorBoard, OpenCV}}{Sept. 2022}
          \resumeItemListStart
            \resumeItem{Built an Age-Invariant Face Recognition model using TensorFlow, trained on CACD. A unified deep architecture performs cross-age face synthesis and recognition simultaneously, removes the requirement of paired data and true age of samples}
            \resumeItem{Extended from auto-encoder based GAN, an Encoder and discriminator pair is used to learn discriminative and robust facial features disentangled from age}
            \resumeItem{Patch-based discriminator with Attention, is used for photorealistic age regressed/progressed face images while guaranteeing robustness to large background complexity}
          \resumeItemListEnd 
          
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------Achievement---------------
\section{Achievements and Awards}
    \resumeItemListStart
       \resumeItem{\textbf{8th} in \href{https://www.formula-ata.it/results-2022/}{\textbf{FS Italy 2022}} Engineering Design Event}
       \resumeItem{\textbf{3rd} in {\href{https://nxpaimindia.com/}{\textbf{NXP AIM India Smart Car Race Challenge}}} and Best Car Model Award from over 400 teams nationally}
       \resumeItem{\textbf{2nd} in {\href{https://www.formulabharat.com/fsev/}{\textbf{FSEV}}} Software and Integration Report}
       \resumeItem{Successfully Passed {\href{https://www.credential.net/385345b4-2736-4fb8-b647-11c777892adf#gs.iud9s8}{\textbf{TensorFlow Developer Certification}}}. A 5-hour rigorous test, testing a candidate’s proficiency in solving Machine learning problems from various domains namely Computer Vision, NLP and Time Series}
       \resumeItem{\textbf{Mr. Personality (Runner-Up)} in annual personality contest}
    \resumeItemListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Java, Arduino, MATLAB/Octave, Bash Scripting, \LaTeX} \\
     \textbf{Framework and Libraries}{: Linux, TensorFlow, Keras, ROS(Robot Operating System), ROS2, OpenCV, Gazebo, pandas, SciKit-learn, Flask, HTML, Bootstrap, NumPy, Matplotlib, SQL} \\
     \textbf{Tools}{: Git, postgres SQL, Anaconda} \\
     \textbf{Soft Skills}{: Leadership, Public Speaking, Strategic Planning} \\
    }}
 \end{itemize}
 % \vspace{-14pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Team Defianz-DTUSDC Racing}{Jan. 2022 -- Present}{Autonomous System Lead}{Delhi Tech. University}
            \resumeItemListStart
                \resumeItem{Personally responsible for acquiring Title Sponsorships from a tech giant like NXP Semiconductors}
                \resumeItem{Responsible for development and Presentation of Autonomous pipeline for Formula Student Italy 2022 driverless competition}
                \resumeItem{Responsible for the system integration of autonomous system into EV and constant review of individual department progress}
                \resumeItem{Carried out recruitment process, managing 10+ new recruits, overlooking their training and turning them into an asset for the team in under 2 months}
            \resumeItemListEnd


        \resumeSubheading{Desh ke Mentor Program}{Jan. 2022 -- Jun. 2022}{Mentee}{Govt. of NCT Delhi}
            \resumeItemListStart
                \resumeItem{Mentored 4 high-school students for 6 months, guiding them through the process of exploring their potential career choices and mentoring them with a plan of action and series of goals through their desired career path}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
